[dcpo_demsupport]

### 2020-07-03 paper/dcpo_demsupport.Rmd
compare n

```{r dcpo_input}
dcpo_input_raw2 <- read_csv("data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
  filter(!(str_detect(item, "army_wvs") & # WVS obs identified as problematic by Claassen 
    ((country=="Albania" & year==1998) |
         (country=="Indonesia" & (year==2001 | year==2006)) |
         (country=="Iran" & year==2000) |
         (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
         (country=="Vietnam" & year==2001)) |
    (str_detect(item, "strong_wvs") &
         ((country=="Egypt" & year==2012) |
              (country=="Iran" & (year==2000 | year==2007)) | # 2005 in Claassen
              (country=="India") |
              (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
              (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
              (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
              (country=="Vietnam" & year==2001))))) %>%
  with_min_yrs(2)

@@

>>>>

```{r dcpo_input}
dcpo_input_raw1 <- read_csv("data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
  filter(!(str_detect(item, "army_wvs") & # WVS obs identified as problematic by Claassen 
    ((country=="Albania" & year==1998) |
         (country=="Indonesia" & (year==2001 | year==2006)) |
         (country=="Iran" & year==2000) |
         (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
         (country=="Vietnam" & year==2001)) |
    (str_detect(item, "strong_wvs") &
         ((country=="Egypt" & year==2012) |
              (country=="Iran" & (year==2000 | year==2007)) | # 2005 in Claassen
              (country=="India") |
              (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
              (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
              (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
              (country=="Vietnam" & year==2001))))) %>%
  with_min_yrs(2)

@@

```{r compare_n}
supdem <- dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>%
  read_csv(col_types = "cdcddcdc")

supdem_ncy <- supdem %>%
  dplyr::select(Country, Year) %>% 
  unique() %>% 
  nrow()

supdem_ncyi <- supdem %>%
  dplyr::select(Country, Year, Item) %>% 
  unique() %>% 
  nrow()

dcpo_input_ncy <- dcpo_input_raw1 %>% 
  dplyr::select(country, year) %>% 
  unique() %>% 
  nrow()

dcpo_input_ncyi <- dcpo_input_raw1 %>% 
  dplyr::select(country, year, item) %>% 
  unique() %>% 
  nrow()

increase_cy <- round((dcpo_input_ncy/supdem_ncy - 1) * 100, 1)
increase_cyi <- round((dcpo_input_ncyi/supdem_ncyi - 1) * 100, 1)
```
